Supplementary material

### 2023-06-26 analyses/scripts/S4_Table.Rmd
Renamed the Rmarkdown supplementary scripts

@@

@@

knitr::kable(cols_7_to_10, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_7_to_10)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

@@

knitr::kable(cols_11_to_14, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_11_to_14)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

@@

knitr::kable(cols_15_to_16, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

@@

@@

@@

knitr::kable(cols_21_to_22, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```

>>>>

## Table 1

This section presents extracted data on the author affiliation type (affiliation_type), 
whether it is a purely academic collaboration (academic_collab), and the location
that was studied.

@@

## Table 2

This section presents extracted data on the disease studied (disease), 
type of objective studied (objectives), whether the paper had an author in
the location studied (author_in_country_studied), and how individuals were 
represented (individual_representation).

@@

knitr::kable(cols_7_to_10, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_7_to_10)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```
## Table 3

This section presents extracted data on whether spatial heterogeneity was
represented (space_representation), the type of model structure 
(model_structure), the type of parametrization and validation method used.

@@

knitr::kable(cols_11_to_14, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    # caption = make_table_caption(cols_11_to_14)
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```
## Table 4

This section presents extracted data on the type of outbreak and the interventions 
studied.

@@

knitr::kable(cols_15_to_16, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```
## Table 5

This section presents extracted data on whether vaccination was modelled as 
a sole intervention for comparison against other interventions 
(vax_modelled_with_non_vax) and the studies' conclusion on the impact of 
vaccination (is_vax_effective).

@@

## Table 6

This section presents extracted data on the outcomes measured and whether a 
sensitivity analysis was conducted.

@@

## Table 7

This section presents extracted data on whether observed data was used for 
model validation (data_used), and whether the data was made available 
(data_available).

@@

knitr::kable(cols_21_to_22, 
    format = "latex", 
    booktabs = TRUE,
    longtable = TRUE
    ) %>% 
  kableExtra::kable_styling(latex_options = c("striped", 
                                  "scale_down", 
                                  "hold_position", 
                                  "repeat_header"),
                            font_size = 9
                ) %>% 
  kableExtra::column_spec(column = c(2, 4), width = "4cm") %>% 
  kableExtra::landscape() 
```
## Table 8

This section presents extracted data on whether the simulation code was made 
available (simulation_code_available) and whether vaccination was modelled 
(vax_modelled).
